---
title: "Lab 3"
author: "Jia Jiang"
format: 
  html:
    self-contained: true
    code-tools: true
    code-fold: true
execute: 
  eval: true
  error: false
  echo: true
  messages: false
  warning: false
editor: visual
---

```{r, message: FALSE, show_col_types = FALSE}

library(tidyverse)
library(here)

surveys <- read_csv(here("hiphop.csv"))

hiphop_clean <- surveys |> 
  mutate(fam = as.factor(familiarity))
hiphop_clean |> 
  distinct(word)
hiphop_clean |> 
  mutate(new_ethnic = case_when(ethnic == "white" ~ "white", 
                                TRUE ~ "non-white"))
hiphop_new <- hiphop_clean |> 
  select(c(sex, 
           age, 
           ethnic, 
           subj)) |> distinct(subj, 
                              .keep_all = TRUE)  

```

2.The data surveys individual musical tastes and correlating that with the familiarity of AAE words. They also include characteristics of the individuals. The contect of the study is to test if preference in music tastes can predict AAE knowlegde. The Variables were recorded through 168 undergrads in University of Minnesota. The sample was selected by who was not african american.

3.The rows are the word, the person, music genre, and the familiarity. Row is a person's response to the familiarity of the word and other factors that may contribute to that familiarity.

4.  It is replaced with NA, unknown, and missing values was replaced by mean values. The benefit is that it actually correlate with missing value instead of just having zero there but the drawback is that you can not do some functions with it. Another benefit would be that it allows us to do math on the row although it was missing values in plot for blackWeekly. But unknown is bad for a data graph that is separated by racial groups because putting them into one group make the graph not cohesive.

6.There is 64 distinct words

8.  because there are more racial groups than white and non-white and grouping all non-whites into a category is racist.

    ```{r}
    ggplot(data =hiphop_new, aes(x=age)) +
      geom_histogram()
    ggplot(data =hiphop_new, aes(x=ethnic)) +
      geom_bar()
    ```

9.  The sex demographic is male/female. The age demographic 18-40. The ethnic is white, asian, african, indian, hispanic, biracial, native. The ethnicities were mostly white and they were mostly in the age range of 20s and that makes sense because it was conducted in a college.

10. 

11.min: catch the vapors max: off the hook

```{r}
hiphop_clean |> 
  group_by(word) |> 
  filter(age<20) |> 
  summarise(avg = mean(familiarity)) |> 
  slice_max(avg)
hiphop_clean |> 
  group_by(word) |> 
  filter(age<20) |> 
  summarise(avg = mean(familiarity)) |> 
  slice_min(avg)
```

12.max : feel me min: break someone out, dukey rope, plex, rollie

```{r}
hiphop_clean |> 
  group_by(word) |> 
  filter(ethnic != "white",
         sex == "Female") |> 
  summarise(avg = mean(familiarity)) |> 
  slice_max(avg)

hiphop_clean |> 
  group_by(word) |> 
  filter(ethnic != "white",
         sex == "Female") |> 
  summarise(avg = mean(familiarity)) |> 
  slice_min(avg)

```

13. max: feel me min:beezy, break someone out, catch the vapors, crossroads, dap, domino, face gator, finna, ghostride, good hair

```{r}
hiphop_clean |> 
  group_by(word) |> 
  filter(ethnic == "white", 
         age>30, 
         sex=="male") |> 
  summarise(avg = mean(familiarity)) |> 
  slice_max(avg)

hiphop_clean |> 
  group_by(word) |> 
  filter(ethnic == "white", 
         age>30, 
         sex=="male") |> 
  summarise(avg = mean(familiarity)) |> 
  slice_min(avg)
```

14.Subject 17 because they match all the filters and knows the most in the beiber option

```{r}
hiphop_clean  |> 
  distinct(subj, 
           .keep_all = TRUE) |> 
  filter(ethnic == "white" ,
         sex == "Male", 
         city < 60000, 
         city > 10000, 
         age > 17, 
         age < 23 ) |>
  slice_max(bieber)
```
